\section{ByLaws}
By-Laws of the Foxboro Homeowners Association
Revision 1/2007


\subsection{ARTICLE I Name of Association}

The Association shall be known as the Foxboro Home Owners’ Association of Brentwood, Tennessee (not for profit organization).

\subsection{ARTICLE II MISSION STATEMENT}

More than a destination at the end of the day, Foxboro is a community
you want to call home and where you feel at home. Our goal will be
achieved when:

Being part of our community means sharing with your neighbors a common
desire to promote harmony and contentment, and the value of living within
the Foxboro community.

The association strikes a reasonable, logical balance between the best
interests of individual homeowners and those of the community as a whole.
Our homeowners and association leaders recognize and accept their rights
and responsibilities.

\subsection{ARTICLE III OFFICES}

The principal office of the Association shall be located at the residence
of the President.

\subsection{ARTICLE IV MEETING OF MEMBERS}

\subsubsection{SECTION 1: Annual Meeting.}

The annual meeting of the Members of the Association shall be held each
year at a date and time fixed by the Board of Directors. The secretary
shall give notice of the annual meeting to all members of record at least
thirty (30) days prior to such meeting specifically outlining the date,
time, and location.

The Board of Directors may designate any place within Brentwood as the
place of meeting for the annual meeting, or any special meeting of the
members of the Association.

\subsubsection{SECTION 2: Order of Business for Annual Meeting.}

\begin{itemize}
\item Call Meeting to Order.

\item Proof of notice of meeting.

\item Reading minutes of last previous annual meeting.

\item Report of Officers.

\item Reports of Committees.

\item Election of Association Board.

\item Such miscellaneous business as may come or be properly brought
before the meeting.

\item Announcements.

\item Adjournment.

\end{itemize}


\subsubsection{SECTION 3: Special Meetings.}
Special meetings of Members for any purpose or purposes, may be called at
any time by the President, or by a majority of the Board of Directors,
and shall be called by the President upon written request of twenty
(20\%) percent of the membership. Business transacted at all special
meetings shall be confined to the subjects or purposes stated in the call.


\subsubsection{SECTION 4: Quorum.}
The presence at the meeting of Members entitled to cast, or of proxies
entitled to cast, 1/10 of the total votes shall constitute a quorum. If,
however, a quorum shall not be present or represented at any meeting,
a majority of the Members so represented may vote to commence the meeting
and transact business of the Association until adjournment.

\subsubsection{SECTION 5: Proxies.}
At all meetings of Members, a Member may vote or give his consent to proxy
executed in writing by the Member. Such proxy shall and must bear a date
not more than five (5) days prior to said meeting, and must be filed with
the secretary of the Association before or at the time of the meeting.

\subsubsection{SECTION 6: Voting of Members.}
Each active member of the Association shall be entitled to one (1) vote
for each household owned. In no event shall more than one vote be cast
with respect to any household. Normal voting shall be by a voice vote,
proxy, or by any method called for by the (a) President, or by (b)
by motion and approval of the majority present.

\subsection{ARTICLE V BOARD OF DIRECTORS}

\subsubsection{SECTION 1: General Powers.}
The management of all the affairs and business of the Association shall
be vested with the Board of Directors. The general responsibilities of
the Board shall include, but not be limited to, the following:

\begin{itemize}
\item Preparing and adopting an annual budget.

\item The establishment of annual dues for the Association.

\item Establish and maintain an adequate reserve fund balance for the
periodic maintenance, repairs and replacement of the improvements to
the common areas or fixed assets, to be maintained out of the annual
dues / assessments.

\item Providing for maintenance, care, and upkeep of all areas, which
are under the responsibility of the Association.

\item Keeping all monies of the Association in a bank depository approved
by the Board, and using the proceeds to administer the Association.

\item Obtaining and carrying insurance against casualties and liabilities,
if deemed necessary by the Board.

\item Paying the cost of all services rendered to the Association.

\item Shall institute, adopt, and maintain policies that protect
the Foxboro community as a whole, while protecting the interests of
individual homeowners.

\item Provide effective community leadership.

\item To encourage and promote social relationships, and greater community
involvement, among the households of the Foxboro community.

\end{itemize}


\subsubsection{SECTION 2: Nomination.}
Nomination for election to the Board of Directors shall be made by
a Nominating Committee, selected by the Board President, or from the
floor at the annual meeting of Members. The Nominating Committee shall
consist of a chairman, who shall be a member of the Board of Directors,
and one or more members of the Association. The committee will nominate
a recommended slate of directors at the annual meeting. All candidates
shall consent to their nomination.

\subsubsection{SECTION 3: Number, Tenure, and Qualifications.}
The number of directors of the association shall not be less than four
(4) persons who shall be elected at the annual meeting of the Members
by a plurality vote of those in attendance with the right to vote in
person or by proxy. The term of office is for one (1) calendar year. Each
director shall hold office until his successor is elected even though
his tenure in office should thereby exceed one (1) year. It shall be
a requirement of the office of director that such person be an active
member of the Association.

\subsubsection{SECTION 4: Election of Officers.}
The directors shall elect at the first Board meeting, after each annual
meeting of the Association, the following officers, from the elected Board
Members, for a term of one (1) calendar year or until their successors
are chose even though their tenure of office would thereby exceed one
(1) year: President, Vice President, Secretary, and Treasurer.

Officers within the Board of Directors will be rotated. No Director
may serve more than three (3) consecutive terms within a specific
office. There are no specified term limits for participation on the
Board of Directors.

\subsubsection{SECTION 5: Quorum.}
A majority of the number of active elected directors (i.e., greater than
50 per cent) shall constitute a quorum for the transaction of business.

\subsubsection{SECTION 6: Vacancies.}
Any vacancy occurring in the Board of Directors, regardless of the manner
in which caused, may be filled by the affirmative vote of the majority
of the remaining directors. A director elected to fill a vacancy shall
be elected for the unexpired term of his predecessor in office.

\subsubsection{SECTION 7: Board Meetings.}
Regular meetings of the Board of Directors shall be held at the call of
the President. Board meetings shall be held at least quarterly during
the calendar year. All meetings of the board are open to all members of
the association.

\subsubsection{SECTION 8: Officers.}
The term and election of officers is set forth in Article V, Section
4. Each officer, whether elected or appointed, shall hold office until
his successor shall have been duly elected. It shall be a requirement
that an officer be a member of the Association.

President:  Shall in general supervise and control all the business
and affairs of the association, subject to the approval of the Board of
Directors. He shall, when present, preside at all meetings of the Members
and of the Board of Directors. The President shall be an ex-officio
member of standing committees and shall be responsible for carrying into
effect all orders and resolutions of the Board of Directors and Members
as required or as good business dictates.

Vice President: Shall exercise the functions of the President in the
event of absence or disability. Shall have such powers and discharge such
duties as may be assigned by the President or by the Board of Directors.

Secretary: Shall keep the minutes of the annual member meeting and of
the Board of Directors meetings in one or more books provide for such
purpose. See that all notices are duly given in accordance with the
Bylaws or as required by the Board of Directors. Be a custodian of
all association records. Keep a register of the mailing addresses of
all members. In general, perform all duties incident to the office of
the Secretary.

Treasurer: Shall have charge and custody of and be responsible for all
monies of the Association; receive and give receipts for monies due and
payable to the Association from any source whatsoever and deposit all such
monies in the name of the Association in such bank as shall be selected
by the Board. Shall render to the Board of Directors, from time to time,
as may be required, an account of all transactions of the Treasurer
and of the financial condition of the Association. The treasurer shall
   disperse funds consistent with the approved annual budget as
approved by the Board of Directors. Any special project, or extraordinary
expenses, will require prior Board approval before disbursement of funds
by the treasurer.

\subsubsection{SECTION 9: Other Board Members.}

Board Members at Large: Shall represent the community as a whole at all
Board Meetings. Will replace any vacancy in the office of Vice President,
Secretary, or treasurer.

Landscape Coordinator: The landscape coordinator shall be responsible
for the development and maintenance of the front entrance to the Foxboro
Community. Shall render to the Board of Directors proposed annual budgets
for approval. All transactions to be approved by Board.

President of Women’s Club: Shall represent the interests of the Foxboro
Women’s Club at all Board Meetings.

\subsubsection{SECTION 10: Standing or Temporary Committees.}
The Board of Directors may appoint standing or temporary committees from
its own number from time to time as deemed appropriate in carrying out
its purpose. All committees so appointed shall keep regular minutes
of the transactions of their meetings and shall record them with the
Secretary of the Association.

\subsubsection{SECTION 11: Official Records.}
The association shall maintain each of the following items, applicable,
which constitute the official records of the association:

\begin{itemize}

\item Minutes. Minutes of all meetings of the members of the association,
and board of directors must be maintained in written form. These minutes
must be maintained for at least 7 years.

\item A copy of the Bylaws of the association and of each amendment.

\item A copy of the Covenants of each section within Foxboro Neighborhood.

\item A current roster of all members and their mailing addresses.

\item All of the association’s insurance policies or a copy thereof,
such policies must be retained for at least 7 years.

\item A current copy of all contracts to which the association is a
party. Bids received by the association for work to be performed are
considered official records and must be kept for a period of 1 year.

\item The financial and accounting records of the association, kept
according to good practices. All financial records must be kept for
a period of at least 7 years. This shall include: accurate, itemized,
and detailed records of all receipts and expenditures.

\end{itemize}

\subsection{Article VI Financial Matters of Association}

\subsubsection{SECTION 1: Financial Reporting.}
The association shall prepare an annual financial report for submission
to the membership at the annual meeting. A copy of the financial report
is available upon request, and shall consist of:

The amount of receipts and expenditures by classification; and
The beginning and ending cash balances of the association.

\subsubsection{SECTION 2: Dues.}

All annual fees are payable on or before March 31st.  The Board of
Directors is empowered to set the annual membership fee based upon the
financial needs of the association. The Board at the annual meeting
shall communicate notice of such changes in the membership dues.

New residents with occupancy prior to July 1 of the calendar year are
required to pay 100\% of the annual dues. New residents with occupancy
after July 1 will be required to pay 50\% of the annual dues. New
residents will be credited with payment, if previous owner has already
paid the annual dues.



\subsubsection{SECTION 3: Deposits.}

All funds of the association shall be deposited to the credit of the
association in a bank depository as selected and approved by the Executive
Board. It is further agreed that the association shall establish and
maintain an adequate reserve fund balance for the periodic maintenance,
repairs and replacement of the improvements to the common areas or
fixed assets, to be maintained out of the annual dues/assessments. Such
minimum balance will be determined and adjusted annually by the Board
of Directors.

\subsubsection{SECTION 4: Assessments.}
The Board of Directors is empowered to issue an assessment to the
membership for specified projects not included within the annual budget
that serve in the best interest of the Foxboro community as a whole. Prior
to the issuance of the assessment, the Board will:

Communicate to the community of homeowners the proposed project to be
included within the assessment.  A preliminary budget for the project
will be submitted to each member.  A special meeting will be conducted
with the membership.

\subsubsection{SECTION 5: Contracts.}
The Board of Directors shall receive competitive bids on all projects
before entering into any contract in the name of the Association. Members
of the Board shall vote in the plurality on the terms of such contract
before execution.

\subsubsection{SECTION 6: Checks, Drafts, etc.}
The Treasurer shall sign all checks, drafts, or other orders for payment
of money, notes or other evidence of indebtedness issued in the name
of the association. The Board may, at its discretion, place financial
limits on the ability of the Treasurer to issue checks.

\subsubsection{SECTION 7: Gifts.}
The Board of Directors may accept on behalf of the Association any
contribution, gift, bequest or devise for the general purposes or for
any special purposes of the Association.

\subsubsection{SECTION 8: Contributions.}
The Association shall not embark upon any program of the issuance of
any funds to charities, special interest groups, clubs, etc. without
the approval by two-thirds vote of the households eligible to vote.

\subsection{Article VII Miscellaneous}

\subsubsection{SECTION 1:}
Any question as to the meaning or proper interpretation of any of the
provisions of these by-laws shall be determined by the Board of Directors
of the Association.

\subsubsection{SECTION 2: Definition of Membership.}
A member of the Association shall be defined as a legal owner of a
household in Foxboro that has paid the current annual Association fees and
is entitled to one (1) vote as outlined in Article IV, Sections 5 \& 6.

\subsubsection{SECTION 3: Major Capital Expenditures.}
Major capital expenditures shall be defined as that expenditure of funds
for the construction of new amenities and/or the replacement of existing
amenities or repairs. The Board of Directors is empowered to approve such
expenditures pursuant to Article V, Section 1 and Article VI, Section 5.

\subsubsection{SECTION 4:}
The Board of Directors of the Association is empowered to amend the
By-Laws of the Association provided approval is by two-thirds of the
active Board of Directors.


